\subsection{Problem Background}

Dancing with the Stars (DWTS) is a popular television competition show where celebrities are partnered with professional dancers and perform dances each week. A panel of expert judges scores each couple's dance, and fans vote for their favorite couple. The judge and fan votes are combined to determine which couple is eliminated each week.

The show has completed 34 seasons, and the method of combining judge scores and fan votes has evolved:
\begin{itemize}
    \item \textbf{Seasons 1-2}: Rank-based method
    \item \textbf{Seasons 3-27}: Percent-based method
    \item \textbf{Seasons 28-34}: Returned to rank-based method, with an additional mechanism where judges choose from the bottom two couples
\end{itemize}

\subsection{Research Objectives}

This study addresses the following key questions:

\begin{enumerate}
    \item \textbf{Fan Vote Estimation}: Develop mathematical models to estimate fan votes (which are unknown and confidential) for each contestant for the weeks they competed.
    
    \item \textbf{Model Validation}: Verify that the estimated fan votes lead to results consistent with actual eliminations, and quantify the uncertainty in these estimates.
    
    \item \textbf{Voting Method Comparison}: Compare and contrast the rank-based and percent-based methods across all seasons, analyzing which method favors fan votes more.
    
    \item \textbf{Controversial Cases}: Examine how different voting methods would have affected controversial cases (e.g., Jerry Rice, Bobby Bones).
    
    \item \textbf{Factor Impact Analysis}: Analyze the impact of professional dancers and celebrity characteristics (age, industry, region) on both judge scores and fan votes.
    
    \item \textbf{New Voting System}: Propose a new voting system that is more "fair" or "exciting" than the current methods.
\end{enumerate}

\subsection{Data Description}

The dataset contains information for 34 seasons of DWTS, including:
\begin{itemize}
    \item Contestant information (name, age, industry, region, professional dancer partner)
    \item Judge scores for each week (1-10 scale)
    \item Season results and final placements
    \item Total of 299 elimination weeks across all seasons
\end{itemize}

\subsection{Report Structure}

This report is organized as follows:
\begin{itemize}
    \item \textbf{Section 2}: Data preprocessing methods
    \item \textbf{Section 3}: Fan vote estimation model and validation
    \item \textbf{Section 4}: Comparison of rank-based and percent-based voting methods
    \item \textbf{Section 5}: Analysis of factor impacts (pro dancers, age, industry, region)
    \item \textbf{Section 6}: Proposal for a new machine learning-based voting system
    \item \textbf{Section 7}: Conclusions and recommendations
\end{itemize}
