\documentclass{mcmthesis}
\mcmsetup{tstyle = \color{red}\bfseries,
          tcn = 2603215, problem = C,
          sheet = true, titleinsheet = true, keywordsinsheet = true,
          titlepage = false, abstract = true}

\usepackage{txfonts}
\usepackage{caption}
\captionsetup[figure]{font=small}
\captionsetup[table]{font=small}
\usepackage{indentfirst}
\usepackage{esint}
\usepackage{subcaption}
\usepackage{floatrow}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}
\usepackage{xcolor}
\usepackage{tabularray}
\usepackage{lastpage}  % 用于显示总页数

\setlength{\headheight}{14pt}
\setcounter{tocdepth}{2}

\title{Data With The Stars: A Comprehensive Analysis of Voting Systems and Fan Engagement}

\date{\today}

\begin{document}

\begin{abstract}
We develop mathematical models to estimate fan votes, compare voting methods, analyze factor impacts, and propose a new machine learning-based voting system for Dancing with the Stars (DWTS).

First, we establish a constrained optimization model for fan vote estimation, achieving 90.0\% accuracy (265/299 weeks) using multi-start SLSQP with differential evolution fallback. Monte Carlo simulation reveals moderate uncertainty (average CV $\approx$ 12\%).

Second, we compare rank-based and percent-based voting methods across all 34 seasons. The percent-based method achieves 97.0\% accuracy (290/299), significantly outperforming the rank-based method (60.5\%, 181/299). In three of four controversial cases, the percent-based method correctly predicted survival.

Third, we analyze factor impacts: professional dancers affect judge scores more than fan votes ($d = 1.24$ vs. $d = 0.68$); age affects both similarly ($d = -0.48$ vs. $d = -0.52$); industry affects fan votes more than judge scores ($d = 1.15$ vs. $d = 0.72$).

Finally, we propose a machine learning-based voting system using LightGBM, achieving 97.99\% accuracy (293/299), a 9.03 percentage point improvement over baseline. The system promotes fairness by automatically considering multiple factors while maintaining excitement through high accuracy and preserved fan vote emphasis (62.7\% importance).

\begin{keywords}
Fan Vote Estimation, Voting Method Comparison, Factor Impact Analysis, Machine Learning, LightGBM
\end{keywords}

\end{abstract}
\maketitle

\tableofcontents
\newpage

\section{Introduction}
\input{sections/introduction}

\section{Data Preprocessing}
\input{sections/stage1_preprocessing}

\section{Fan Vote Estimation Model}
\input{sections/stage2_fan_vote_estimation}

\section{Comparison of Voting Aggregation Methods}
\input{sections/stage3_voting_comparison}

\section{Factor Impact Analysis}
\input{sections/stage4_factor_impact}

\section{Proposed New Voting System}
\input{sections/stage5_new_system}

\section{Conclusions and Recommendations}
\input{sections/conclusions}

\newpage
\section*{Memo to Producers}
\addcontentsline{toc}{section}{Memo to Producers}
\input{sections/memo_to_producers}

\newpage
\section*{References}
\addcontentsline{toc}{section}{References}
\input{sections/references}

\newpage
\section*{AI Use Report}
\addcontentsline{toc}{section}{AI Use Report}
\input{sections/ai_use_report}

\label{LastPage}  % 标记最后一页，用于页码显示

\end{document}
